data wrangling and plots

### 2021-03-03 shared analysis files /data_wrangling_plot22feb.Rmd
adding in full model with response variable as a mod, officially removing CT assays from dataset

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_MA_ES<-dat_MA_ES %>% filter (!is.na(yi))

@@

#removing outlier point to get better picture of data structure AND excluding CT assays 
normalized <- dat_MA_ES %>%
  filter(yi > -20, resp_units != "C") 
#filtering for studies with common variable g 
common_unit_g <-dat_MA_ES %>% 
filter(resp_def == "body mass")
#filtering for genus to only be drosophila 
drosophila <- dat_MA_ES %>% 
  filter(genus == "Drosophila")
#filtering for just flux ranges of 10 C 
common_range <- dat_MA_ES %>% 
  filter(flux_range == "10")
#filtering for just studies with mean temp of 24
common_temp <- dat_MA_ES %>% 
  filter(mean_temp_constant == "24")
```

@@

## Question how does scale (life or org level) affect response?
### Figure 11. 
```{r, message=FALSE}
#boxplot
ggplot(normalized, aes(x=exp_age, y=yi, color = as.factor(exp_age)))+
  geom_boxplot()+
  theme_bw()+
  ggtitle("SMD across different experimental ages")

@@

## Question: How does response variable affect response?
### Figure 14.
```{r, message=FALSE}
#plot across studies with common response variable body mass
ggplot(common_unit_g, aes(y=yi, color=as.factor(flux_range), x = study_id))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
  ggtitle("SMD across fluctuation ranges colored by studies with the common unit grams")
#random effects model within subset data
fig14 <- rma.mv(yi, vi, data=common_unit_g,
               random = ~1 | experiment_id/ study_id,
                 method="REML") 
fig14
#simple linear model looking at how flux_range affects yi within subset data
simple14<-lm(yi~study_id, data =common_unit_g)
summary(simple14)
```

>>>>

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_MA_ES<-dat_MA_ES %>% 
  filter (!is.na(yi)) %>%
  filter(resp_units != "C")

@@

#removing outlier point to get better picture of data structure AND excluding CT assays 
normalized <- dat_MA_ES %>%
  filter(yi > -20) 
#filtering for studies with common variable g 
common_unit_g <-dat_MA_ES %>% 
filter(resp_def == "body mass")
#filtering for genus to only be drosophila 
drosophila <- dat_MA_ES %>% 
  filter(genus == "Drosophila")
#filtering for just flux ranges of 10 C 
common_range <- dat_MA_ES %>% 
  filter(flux_range == "10")
#filtering for just studies with mean temp of 24
common_temp <- dat_MA_ES %>% 
  filter(mean_temp_constant == "24")
```

@@

## Question how does scale (life or org level) affect response?
### Figure 11.

```{r, message=FALSE}
#boxplot
ggplot(normalized, aes(x=exp_age, y=yi, color = as.factor(exp_age)))+
  geom_boxplot()+
  theme_bw()+
  ggtitle("SMD across different experimental ages")

@@

## Question: How does response variable affect response?
### Figure 14.
```{r}
#full random effects model looking at all the responses in the entire dataset
response_variable_mod <- rma.mv(yi, vi, data=dat_MA_ES, mods = ~resp_def, 
               random = ~1 | experiment_id/ study_id/ response_id,
                 method="REML") 
response_variable_mod

#full random effects model looking at all the response units in the entire dataset
response_units_mod <- rma.mv(yi, vi, data=dat_MA_ES, mods = ~resp_units, 
               random = ~1 | experiment_id/ study_id /response_id,
                 method="REML") 
response_units_mod
```

```{r, message=FALSE}
#plot across studies with common response variable body mass
ggplot(common_unit_g, aes(y=yi, color=as.factor(flux_range), x = study_id))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
  ggtitle("SMD across fluctuation ranges colored by studies with the common unit grams")
#random effects model within subset data
fig14 <- rma.mv(yi, vi, data=common_unit_g,
               random = ~1 | experiment_id/ study_id,
                 method="REML") 
fig14
#simple linear model looking at how flux_range affects yi within subset data
simple14<-lm(yi~study_id, data =common_unit_g)
summary(simple14)
```
